New cardinality estimation algorithms for HyperLogLog sketches

### 2017-01-06 paper/paper.tex
improved description of joint estimation algorithm, redefined phi

\subsection{Computation of the maximum likelihood estimates}
The maximum likelihood estimates can be obtained by maximizing \eqref{equ:log_likelihood_pair}. Since the three parameters are all non-negative, this is a constrained optimization problem. In order to get rid of these constraints, we use the transformation $\symPoissonRate=\symNumReg e^{\symPhi}$. This mapping has also the nice property that relative accuracy limits are translated into absolute ones, because $\Delta\symPhi = \Delta\symPoissonRate/\symPoissonRate$. Many optimization algorithm implementations allow the definition of absolute limits rather than relative ones.

The transformed log-likelihood function can be written as
\begin{multline}
\label{equ:max_likelihood_phi_func}
\symFunc(\symPhi_\symSetASuffix,\symPhi_\symSetBSuffix,\symPhi_\symSetXSuffix):=
\log \symLikelihood(
\symNumReg e^{\symPhi_\symSetASuffix},
\symNumReg e^{\symPhi_\symSetBSuffix},
\symNumReg e^{\symPhi_\symSetXSuffix}
\vert
\boldsymbol{\symRegValVariate}_1,
\boldsymbol{\symRegValVariate}_2
)=
\\
\begin{aligned}
&+
\sum_{\symRegVal=1}^{\symRegRange}
\symCountVariate^{<}_{1\symRegVal}
\log\!\left(
\symZ_{\symSetXSuffix\symRegVal}
+
\symY_{\symSetXSuffix\symRegVal}
\symZ_{\symSetASuffix\symRegVal}
\right)
+
\symCountVariate^{<}_{2\symRegVal}
\log\!\left(
\symZ_{\symSetXSuffix\symRegVal}
+
\symY_{\symSetXSuffix\symRegVal}
\symZ_{\symSetBSuffix\symRegVal}
\right)
\\
&+
\sum_{\symRegVal=1}^{\symRegRange}
\symCountVariate^{>}_{1\symRegVal}
\log\!\left(
\symZ_{\symSetASuffix\symRegVal}
\right)
+
\symCountVariate^{>}_{2\symRegVal}
\log\!\left(
\symZ_{\symSetBSuffix\symRegVal}
\right)
+
\symCountVariate^{=}_{\symRegVal}
\log\!\left(
\symZ_{\symSetXSuffix\symRegVal}
+
\symY_{\symSetXSuffix\symRegVal}
\symZ_{\symSetASuffix\symRegVal}
\symZ_{\symSetBSuffix\symRegVal}
\right)
\\
&+
\symCountVariate^{>}_{1,\symRegRange+1}
\log\!\left(
\symZ_{\symSetASuffix\symRegRange}
\right)
+
\symCountVariate^{>}_{2,\symRegRange+1}
\log\!\left(
\symZ_{\symSetBSuffix\symRegRange}
\right)
+
\symCountVariate^{=}_{\symRegRange+1}
\log\!\left(
\symZ_{\symSetXSuffix\symRegRange}
+
\symY_{\symSetXSuffix\symRegRange}
\symZ_{\symSetASuffix\symRegRange}
\symZ_{\symSetBSuffix\symRegRange}
\right)
\\
&-
\sum_{\symRegVal=0}^{\symRegRange}
\left(
  \symCountVariate^{<}_{1\symRegVal}+
  \symCountVariate^{=}_{\symRegVal}+
  \symCountVariate^{>}_{1\symRegVal}
\right)
\symX_{\symSetASuffix\symRegVal}
+
\left(
  \symCountVariate^{<}_{2\symRegVal}+
  \symCountVariate^{=}_{\symRegVal}+
  \symCountVariate^{>}_{2\symRegVal}
\right)
\symX_{\symSetBSuffix\symRegVal}
+
\left(
  \symCountVariate^{<}_{1\symRegVal}+
  \symCountVariate^{=}_{\symRegVal}+
  \symCountVariate^{<}_{2\symRegVal}
\right)
\symX_{\symSetXSuffix\symRegVal}
.
\end{aligned}
\end{multline}
Here we introduced the following expressions for simplification:
\begin{equation}
\label{equ:definition_xyz}
\symX_{\ast\symRegVal} :=\frac{e^{\symPhi_\ast}}{2^{\symRegVal}},\quad
\symY_{\ast\symRegVal} := e^{-\symX_{\ast\symRegVal}},\quad
\symZ_{\ast\symRegVal} := 1 - \symY_{\ast\symRegVal}.
\end{equation}

@@

\cref{alg:joint_cardinality_estimation} demonstrates the calculation of the estimates given $\boldsymbol\symCountVariate^{>}_{1}$,
$\boldsymbol\symCountVariate^{<}_{1}$,
$\boldsymbol\symCountVariate^{>}_{2}$,
$\boldsymbol\symCountVariate^{<}_{2}$, and
$\boldsymbol\symCountVariate^{=}$. First, a case is distinguished, where
all registers have a value equal to zero in at least one of both HyperLogLog sketches, that is $\symCountVariate^{<}_{10}+\symCountVariate^{=}_0+\symCountVariate^{<}_{20} = \symNumReg$. In this case it is certain that the HyperLogLog sketches represent disjoint sets and their corresponding  cardinality estimates can be  used for $\symPoissonRateEstimate_{\symSetASuffix}$ and $\symPoissonRateEstimate_{\symSetBSuffix}$, respectively.

%TODO

%The initial guess values are important to ensure fast convergence of the optimization algorithm. An obvious choice are the cardinality estimates obtained by using the conventional approach \eqref{equ:conventional_approach}.

%As demonstrated by we In all other cases, the maximum likelihood estimates for $\symPoissonRate_\symSetASuffix$, $\symPoissonRate_\symSetBSuffix$, and $\symPoissonRate_\symSetXSuffix$ will be non-zero. We use the conventional approach to get start values for the estimates of $\symPoissonRate_\symSetASuffix$, $\symPoissonRate_\symSetBSuffix$, and $\symPoissonRate_\symSetXSuffix$, respectively. However, in order to ensure that the values are positive we restrict them to values greater than or equal to 1.

For the general case the Broyden-Fletcher-Goldfarb-Shanno (BFGS) algorithm \cite{Press2007} can be applied, which is a very popular algorithm for non-linear optimization problems. In particular, we used the implementation provided by the Dlib C++ library \cite{King2009}.

\begin{algorithm}
\caption{Joint cardinality estimation.}
\label{alg:joint_cardinality_estimation}
\begin{algorithmic}
\Function {EstimateCardinalities}
{
$\boldsymbol\symCountVariate^{>}_{1}$,
$\boldsymbol\symCountVariate^{<}_{1}$,
$\boldsymbol\symCountVariate^{>}_{2}$,
$\boldsymbol\symCountVariate^{<}_{2}$,
$\boldsymbol\symCountVariate^{=}$
}
\State $\symNumReg\gets
\left\Vert\boldsymbol\symCountVariate^{<}_{1} + \boldsymbol\symCountVariate^{=} + \boldsymbol\symCountVariate^{>}_{1}\right\Vert_1$
\State $\symPoissonRateEstimate_{\symSetASuffix\symSetXSuffix} \gets$ \Call{EstimateCardinality}{$\boldsymbol\symCountVariate^{<}_{1} + \boldsymbol\symCountVariate^{=} + \boldsymbol\symCountVariate^{>}_{1}$}
\State $\symPoissonRateEstimate_{\symSetBSuffix\symSetXSuffix} \gets$ \Call{EstimateCardinality}{$\boldsymbol\symCountVariate^{<}_{2} + \boldsymbol\symCountVariate^{=} + \boldsymbol\symCountVariate^{>}_{2}$}
\If{$\symCountVariate^{<}_{10}+\symCountVariate^{=}_0+\symCountVariate^{<}_{20} = \symNumReg$}
\State $\symPoissonRateEstimate_{\symSetASuffix}\gets
\symPoissonRateEstimate_{\symSetASuffix\symSetXSuffix},\ 
\symPoissonRateEstimate_{\symSetBSuffix}\gets
\symPoissonRateEstimate_{\symSetBSuffix\symSetXSuffix},\
\symPoissonRateEstimate_{\symSetXSuffix}\gets0$
\comm{0.27}{in this case $\symSetS_1\cap\symSetS_2 = \symSetX = \emptyset$ holds}
\State \textbf{return} $(
\symPoissonRateEstimate_{\symSetASuffix},
\symPoissonRateEstimate_{\symSetBSuffix},
\symPoissonRateEstimate_{\symSetXSuffix}
)$
\EndIf
\State $\symPoissonRateEstimate_{\symSetASuffix\symSetBSuffix\symSetXSuffix} \gets$ \Call{EstimateCardinality}{$\boldsymbol\symCountVariate^{>}_{1} + \boldsymbol\symCountVariate^{=} + \boldsymbol\symCountVariate^{>}_{2}$}
\State $\symPhi_\symSetASuffix \gets \log(\max(1, \symPoissonRateEstimate_{\symSetASuffix\symSetBSuffix\symSetXSuffix} - \symPoissonRateEstimate_{\symSetBSuffix\symSetXSuffix})/\symNumReg)$
\State $\symPhi_\symSetBSuffix \gets \log(\max(1, \symPoissonRateEstimate_{\symSetASuffix\symSetBSuffix\symSetXSuffix} - \symPoissonRateEstimate_{\symSetASuffix\symSetXSuffix})/\symNumReg)$
\State $\symPhi_\symSetXSuffix \gets \log(\max(1,
\symPoissonRateEstimate_{\symSetASuffix\symSetXSuffix}+
\symPoissonRateEstimate_{\symSetBSuffix\symSetXSuffix}
-
\symPoissonRateEstimate_{\symSetASuffix\symSetBSuffix\symSetXSuffix})/\symNumReg)$
\State $\symStopDelta\gets\symStopEpsilon/\sqrt{\symNumReg}$
\comm{0.27}{$\symStopEpsilon = 10^{-2}$}
\Repeat
\State 
$
\symPhi'_\symSetASuffix\gets\symPhi_\symSetASuffix,\ \symPhi'_\symSetBSuffix\gets\symPhi_\symSetBSuffix,\  \symPhi'_\symSetXSuffix\gets\symPhi_\symSetXSuffix$
\State
$
\symPhi_\symSetASuffix,
\symPhi_\symSetBSuffix,
\symPhi_\symSetXSuffix
\gets$
\Call{OptimizationStep}{$\symPhi_\symSetASuffix,
\symPhi_\symSetBSuffix,
\symPhi_\symSetXSuffix;
\symFunc,
\nabla\symFunc
$}
\comm{0.27}{e.g. BFGS update step}
\Until{
$\max(
\left|\symPhi_\symSetASuffix - \symPhi'_\symSetASuffix\right|,
\left|\symPhi_\symSetBSuffix - \symPhi'_\symSetBSuffix\right|,
\left|\symPhi_\symSetXSuffix - \symPhi'_\symSetXSuffix\right|) \leq \symStopDelta
$}
\State 
$
\symPoissonRateEstimate_{\symSetASuffix}
\gets \symNumReg e^{\symPhi_\symSetASuffix},\ \symPoissonRateEstimate_{\symSetBSuffix}
\gets \symNumReg e^{\symPhi_\symSetBSuffix},\ 
\symPoissonRateEstimate_{\symSetXSuffix}
\gets \symNumReg e^{\symPhi_\symSetXSuffix}
$
\State \textbf{return} $(
\symPoissonRateEstimate_{\symSetASuffix},
\symPoissonRateEstimate_{\symSetBSuffix},
\symPoissonRateEstimate_{\symSetXSuffix}
)$
\EndFunction
\end{algorithmic}
\end{algorithm}

>>>>

\subsection{Computation of the maximum likelihood estimates}
The maximum likelihood estimates can be obtained by maximizing \eqref{equ:log_likelihood_pair}. Since the three parameters are all non-negative, this is a constrained optimization problem. In order to get rid of these constraints, we use the transformation $\symPoissonRate=e^{\symPhi}$. This mapping has also the nice property that relative accuracy limits are translated into absolute ones, because $\Delta\symPhi = \Delta\symPoissonRate/\symPoissonRate$. Many optimization algorithm implementations allow the definition of absolute limits rather than relative ones.

The transformed log-likelihood function can be written as
\begin{multline}
\label{equ:max_likelihood_phi_func}
\symFunc(\symPhi_\symSetASuffix,\symPhi_\symSetBSuffix,\symPhi_\symSetXSuffix):=
\log \symLikelihood(
e^{\symPhi_\symSetASuffix},
e^{\symPhi_\symSetBSuffix},
e^{\symPhi_\symSetXSuffix}
\vert
\boldsymbol{\symRegValVariate}_1,
\boldsymbol{\symRegValVariate}_2
)=
\\
\begin{aligned}
&+
\sum_{\symRegVal=1}^{\symRegRange}
\symCountVariate^{<}_{1\symRegVal}
\log\!\left(
\symZ_{\symSetXSuffix\symRegVal}
+
\symY_{\symSetXSuffix\symRegVal}
\symZ_{\symSetASuffix\symRegVal}
\right)
+
\symCountVariate^{<}_{2\symRegVal}
\log\!\left(
\symZ_{\symSetXSuffix\symRegVal}
+
\symY_{\symSetXSuffix\symRegVal}
\symZ_{\symSetBSuffix\symRegVal}
\right)
\\
&+
\sum_{\symRegVal=1}^{\symRegRange}
\symCountVariate^{>}_{1\symRegVal}
\log\!\left(
\symZ_{\symSetASuffix\symRegVal}
\right)
+
\symCountVariate^{>}_{2\symRegVal}
\log\!\left(
\symZ_{\symSetBSuffix\symRegVal}
\right)
+
\symCountVariate^{=}_{\symRegVal}
\log\!\left(
\symZ_{\symSetXSuffix\symRegVal}
+
\symY_{\symSetXSuffix\symRegVal}
\symZ_{\symSetASuffix\symRegVal}
\symZ_{\symSetBSuffix\symRegVal}
\right)
\\
&+
\symCountVariate^{>}_{1,\symRegRange+1}
\log\!\left(
\symZ_{\symSetASuffix\symRegRange}
\right)
+
\symCountVariate^{>}_{2,\symRegRange+1}
\log\!\left(
\symZ_{\symSetBSuffix\symRegRange}
\right)
+
\symCountVariate^{=}_{\symRegRange+1}
\log\!\left(
\symZ_{\symSetXSuffix\symRegRange}
+
\symY_{\symSetXSuffix\symRegRange}
\symZ_{\symSetASuffix\symRegRange}
\symZ_{\symSetBSuffix\symRegRange}
\right)
\\
&-
\sum_{\symRegVal=0}^{\symRegRange}
\left(
  \symCountVariate^{<}_{1\symRegVal}+
  \symCountVariate^{=}_{\symRegVal}+
  \symCountVariate^{>}_{1\symRegVal}
\right)
\symX_{\symSetASuffix\symRegVal}
+
\left(
  \symCountVariate^{<}_{2\symRegVal}+
  \symCountVariate^{=}_{\symRegVal}+
  \symCountVariate^{>}_{2\symRegVal}
\right)
\symX_{\symSetBSuffix\symRegVal}
+
\left(
  \symCountVariate^{<}_{1\symRegVal}+
  \symCountVariate^{=}_{\symRegVal}+
  \symCountVariate^{<}_{2\symRegVal}
\right)
\symX_{\symSetXSuffix\symRegVal}
.
\end{aligned}
\end{multline}
Here we introduced the following expressions for simplification:
\begin{equation}
\label{equ:definition_xyz}
\symX_{\ast\symRegVal} :=\frac{e^{\symPhi_\ast}}{\symNumReg 2^{\symRegVal}},\quad
\symY_{\ast\symRegVal} := e^{-\symX_{\ast\symRegVal}},\quad
\symZ_{\ast\symRegVal} := 1 - \symY_{\ast\symRegVal}.
\end{equation}

@@

\cref{alg:joint_cardinality_estimation} demonstrates the calculation of the estimates given the register values $\boldsymbol\symRegValVariate_{1}$ and 
$\boldsymbol\symRegValVariate_{2}$ of both HyperLogLog sketches. First, the sufficient statistic consisting of $\boldsymbol\symCountVariate^{>}_{1}$,
$\boldsymbol\symCountVariate^{<}_{1}$,
$\boldsymbol\symCountVariate^{>}_{2}$,
$\boldsymbol\symCountVariate^{<}_{2}$, and
$\boldsymbol\symCountVariate^{=}$ is extracted. Next, a case is distinguished, where
all registers have a value equal to zero in at least one of both HyperLogLog sketches, that is $\symCountVariate^{<}_{10}+\symCountVariate^{=}_0+\symCountVariate^{<}_{20} = \symNumReg$. In this case it is certain that the HyperLogLog sketches represent disjoint sets and their corresponding  cardinality estimates can be  used for $\symPoissonRateEstimate_{\symSetASuffix}$ and $\symPoissonRateEstimate_{\symSetBSuffix}$, respectively.

For the general case, the three-dimensional function $\symFunc(\symPhi_\symSetASuffix,\symPhi_\symSetBSuffix,\symPhi_\symSetXSuffix)$ needs to be optimized numerically. A very popular algorithm for such non-linear optimization problems is the Broyden-Fletcher-Goldfarb-Shanno (BFGS) algorithm \cite{Press2007}. In particular, we used the implementation provided by the Dlib C++ library \cite{King2009}. Good initial guess values are important to ensure fast convergence for the optimization algorithm. An obvious choice are the cardinality estimates obtained by the conventional approach \eqref{equ:conventional_approach}. However, in order to ensure that their logarithms are defined, we require that the initial values are not smaller than 1. Within the optimization loop the function $\symFunc$ and its gradient $\nabla\symFunc$ need to evaluated using \eqref{equ:max_likelihood_phi_func} and \eqref{equ:df_dphi} as needed by the optimization algorithm. The optimization loop is continued as long as the absolute change of at least one parameter is larger than a predefined threshold. The threshold is again set proportional to $1/\sqrt{\symNumReg}$ (compare \cref{sec:comp_ml_estimate}).

\begin{algorithm}
\caption{Joint cardinality estimation.}
\label{alg:joint_cardinality_estimation}
\begin{algorithmic}
\Function {EstimateCardinalities}
{
$\boldsymbol\symRegValVariate_{1}$,
$\boldsymbol\symRegValVariate_{2}$
}
\comm{.32}{$\boldsymbol{\symRegValVariate}_1,\boldsymbol{\symRegValVariate}_2\in\lbrace 0,1,\ldots,\symRegRange+1\rbrace^\symNumReg$}
\State 
$\boldsymbol\symCountVariate^{>}_{1}\gets 0$,
$\boldsymbol\symCountVariate^{<}_{1}\gets 0$,
$\boldsymbol\symCountVariate^{>}_{2}\gets 0$,
$\boldsymbol\symCountVariate^{<}_{2}\gets 0$,
$\boldsymbol\symCountVariate^{=}\gets 0$
\comm{.32}{$\boldsymbol\symCountVariate^{>}_{1},
\boldsymbol\symCountVariate^{<}_{1},
\boldsymbol\symCountVariate^{>}_{2},
\boldsymbol\symCountVariate^{<}_{2},
\boldsymbol\symCountVariate^{=}\\\in\lbrace 0, 1, \ldots,\symNumReg\rbrace^{\symRegRange+1}$}
\For{$\symIndexI\gets 1, \symNumReg$}
\If{$\symRegValVariate_{1\symIndexI}
<
\symRegValVariate_{2\symIndexI}$}
\State $\symCountVariate^{<}_{1\symRegValVariate_{1\symIndexI}}
\gets
\symCountVariate^{<}_{1\symRegValVariate_{1\symIndexI}}+1$
\State
$\symCountVariate^{>}_{2\symRegValVariate_{2\symIndexI}}
\gets
\symCountVariate^{>}_{2\symRegValVariate_{2\symIndexI}}+1$
\ElsIf{$\symRegValVariate_{1\symIndexI}
>
\symRegValVariate_{2\symIndexI}$}
\State $\symCountVariate^{>}_{1\symRegValVariate_{1\symIndexI}}
\gets
\symCountVariate^{>}_{1\symRegValVariate_{1\symIndexI}}+1$
\State
$\symCountVariate^{<}_{2\symRegValVariate_{2\symIndexI}}
\gets
\symCountVariate^{<}_{2\symRegValVariate_{2\symIndexI}}+1$
\Else
\State $\symCountVariate^{=}_{\symRegValVariate_{1\symIndexI}}
\gets
\symCountVariate^{=}_{1\symRegValVariate_{1\symIndexI}}+1$
\EndIf
\EndFor
\State $\symPoissonRateEstimate_{\symSetASuffix\symSetXSuffix} \gets$ \Call{EstimateCardinality}{$\boldsymbol\symCountVariate^{<}_{1} + \boldsymbol\symCountVariate^{=} + \boldsymbol\symCountVariate^{>}_{1}$}
\comm{0.32}{use \cref{alg:corrected_raw_estimation} or \ref{alg:estimate_ml}}
\State $\symPoissonRateEstimate_{\symSetBSuffix\symSetXSuffix} \gets$ \Call{EstimateCardinality}{$\boldsymbol\symCountVariate^{<}_{2} + \boldsymbol\symCountVariate^{=} + \boldsymbol\symCountVariate^{>}_{2}$}
\If{$\symCountVariate^{<}_{10}+\symCountVariate^{=}_0+\symCountVariate^{<}_{20} = \symNumReg$}
\comm{0.32}{$\Leftrightarrow\min(\symRegValVariate_{1\symIndexI},\symRegValVariate_{2\symIndexI})=0\ \forall\symIndexI$}
\State $\symPoissonRateEstimate_{\symSetASuffix}\gets
\symPoissonRateEstimate_{\symSetASuffix\symSetXSuffix},\ 
\symPoissonRateEstimate_{\symSetBSuffix}\gets
\symPoissonRateEstimate_{\symSetBSuffix\symSetXSuffix},\
\symPoissonRateEstimate_{\symSetXSuffix}\gets0$
\State \textbf{return} $(
\symPoissonRateEstimate_{\symSetASuffix},
\symPoissonRateEstimate_{\symSetBSuffix},
\symPoissonRateEstimate_{\symSetXSuffix}
)$
\EndIf

%\If{$\boldsymbol\symCountVariate^{>}_{1} = 0$}
%\comm{0.27}{$\symRegValVariate_{1\symIndexI}\leq
%\symRegValVariate_{2\symIndexI}\ \forall\symIndexI$}
%\EndIf

%\If{$\boldsymbol\symCountVariate^{>}_{2} = 0$}
%\comm{0.27}{$\symRegValVariate_{2\symIndexI}\leq
%\symRegValVariate_{1\symIndexI}\ \forall\symIndexI$}
%\EndIf

\State $\symPoissonRateEstimate_{\symSetASuffix\symSetBSuffix\symSetXSuffix} \gets$ \Call{EstimateCardinality}{$\boldsymbol\symCountVariate^{>}_{1} + \boldsymbol\symCountVariate^{=} + \boldsymbol\symCountVariate^{>}_{2}$}
\State $\symPhi_\symSetASuffix \gets \log(\max(1, \symPoissonRateEstimate_{\symSetASuffix\symSetBSuffix\symSetXSuffix} - \symPoissonRateEstimate_{\symSetBSuffix\symSetXSuffix}))$
\State $\symPhi_\symSetBSuffix \gets \log(\max(1, \symPoissonRateEstimate_{\symSetASuffix\symSetBSuffix\symSetXSuffix} - \symPoissonRateEstimate_{\symSetASuffix\symSetXSuffix}))$
\State $\symPhi_\symSetXSuffix \gets \log(\max(1,
\symPoissonRateEstimate_{\symSetASuffix\symSetXSuffix}+
\symPoissonRateEstimate_{\symSetBSuffix\symSetXSuffix}
-
\symPoissonRateEstimate_{\symSetASuffix\symSetBSuffix\symSetXSuffix}))$
\State $\symStopDelta\gets\symStopEpsilon/\sqrt{\symNumReg}$
\comm{0.32}{$\symStopEpsilon = 10^{-2}$}
\Repeat
\comm{0.32}{start optimization}
\State 
$
\symPhi'_\symSetASuffix\gets\symPhi_\symSetASuffix,\ \symPhi'_\symSetBSuffix\gets\symPhi_\symSetBSuffix,\  \symPhi'_\symSetXSuffix\gets\symPhi_\symSetXSuffix$
\State
$
\symPhi_\symSetASuffix,
\symPhi_\symSetBSuffix,
\symPhi_\symSetXSuffix
\gets$
\Call{OptimizationStep}{$\symPhi_\symSetASuffix,
\symPhi_\symSetBSuffix,
\symPhi_\symSetXSuffix
$}
\comm{0.32}{calculate $\symFunc$ and
$\nabla\symFunc$ as needed by optimizer using \eqref{equ:max_likelihood_phi_func} and \eqref{equ:df_dphi},
respectively
}
\Until{
$\max(
\left|\symPhi_\symSetASuffix - \symPhi'_\symSetASuffix\right|,
\left|\symPhi_\symSetBSuffix - \symPhi'_\symSetBSuffix\right|,
\left|\symPhi_\symSetXSuffix - \symPhi'_\symSetXSuffix\right|) \leq \symStopDelta
$}
\comm{0.32}{stop criterion}
\State 
$
\symPoissonRateEstimate_{\symSetASuffix}
\gets e^{\symPhi_\symSetASuffix},\ \symPoissonRateEstimate_{\symSetBSuffix}
\gets e^{\symPhi_\symSetBSuffix},\ 
\symPoissonRateEstimate_{\symSetXSuffix}
\gets e^{\symPhi_\symSetXSuffix}
$
\State \textbf{return} $(
\symPoissonRateEstimate_{\symSetASuffix},
\symPoissonRateEstimate_{\symSetBSuffix},
\symPoissonRateEstimate_{\symSetXSuffix}
)$
\EndFunction
\end{algorithmic}
\end{algorithm}
